### 2023-12-22 main.tex
New Formula Corollary 2

	\sum_{m=0}^{L}\;\sum_{1\leq x_{1}<x_{2}<\ldots<x_{m}\leq L}\left(\prod_{x\notin\{x_{1},\ldots,x_{m}\}}\delta_{\tau_{x},N}\right)\sum_{b_{1},\ldots,b_{m}=1}^{N-1}\left(\prod_{k=1}^{m}\delta_{\tau_{x_{k}},b_{k}}-\delta_{\tau_{x_{k}},N}\right)\mathbb{E}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{Y_{x_{k}}=b_{k}\}}\right]

@@

 	Here we have only one term corresponding to $m=2$ in formula  \eqref{implicit-mass-function}.

@@

	{\color{blue}Here in the last equality we have two terms: the first corresponding to $m=1$ (with $x_{1}=1$) and the second corresponding to $m=2$ in formula \eqref{implicit-mass-function}.}

@@

 	{\color{blue}Here in the last equality we have four terms: the first term corresponds to $m=0$, the second and the third term correspond to $m=1$ (with $x_{1}=1$ and $x_{1}=2$ respectively) and the fourth term corresponds to $m=2$ in formula \eqref{implicit-mass-function}. }

@@

{\color{blue}In the right-hand-side of the equation above the first addend is the product of the indicator of $\ell$ sites, since none of the empty sites of the configuration $\bm{\tau}$ has been considered. Similarly, the second addend is the product of the indicator of $\ell+1$ sites. Indeed, in addition to the $\ell$ occupied sites of $\bm{\tau}$ one empty site is in turn chosen and its hole is filled with all possible particles. In the next addends the idea is repeated with $2,3,...L-\ell$ empty sites in turn filled with all possible particles. We notice that the exponent of the factors (-1) is given by the number of holes that have been turned into particles. Then, we introduce an index $m\in \{\ell,\ell+1,\ldots,L\}$ that counts the number of correlated sites. For each $m$ we introduce the coordinates $1\leq x_{1}<x_{2}<\ldots<x_{m}\leq L$. Then, we associate to to each of these $m$ one of the addend in \eqref{sum}. In particular, for $m=\ell$ we associate the first addend and we rewrite it as
		\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{Y_{x}=\tau_{x}\}}=&\sum_{1\leq x_{1}<\ldots<x_{\ell}\leq L}\;\left(\prod_{k=1}^{\ell}(1-\delta_{\tau_{x_{k}},N})\right)\sum_{b_{1},\ldots,b_{\ell}=1}^{N-1}\left(\prod_{k=1}^{\ell}\delta_{\tau_{x_{k}},b_{k}}\right)\left(\prod_{k=1}^{\ell}\mathbbm{1}_{\{Y_{x_{k}}=b_{k}\}}\right)\nonumber
	\\	=&
		\sum_{1\leq x_{1}<\ldots<x_{\ell}\leq L}\;\left(\prod_{x\notin \{x_{1},\ldots,x_{\ell}\}}\delta_{\tau_{x},N}\right)\sum_{b_{1},\ldots,b_{\ell}=1}^{N-1}\left(\prod_{k=1}^{\ell}\delta_{\tau_{x_{k}},b_{k}}-\delta_{\tau_{x_{k},N}}\right)\left(\prod_{k=1}^{\ell}\mathbbm{1}_{\{Y_{x_{k}}=b_{k}\}}\right)
	Similarly, the second addend in \eqref{sum} is associate to $m=\ell +1$ and it is rewritten as 

@@

		\sum_{1\leq x_{1}<\ldots<x_{\ell+1}\leq L}\;\left(\prod_{x\notin \{x_{1},\ldots,x_{\ell+1}\}}\delta_{\tau_{x},N}\right)\sum_{b_{1},\ldots,b_{\ell+1}=1}^{N-1}\left(\prod_{k=1}^{\ell}\delta_{\tau_{x_{k}},b_{k}}-\delta_{\tau_{x_{k},N}}\right)\left(\prod_{k=1}^{\ell+1}\mathbbm{1}_{\{Y_{x_{k}}=b_{k}\}}\right)

@@

\sum_{m=\ell}^{L}\;\sum_{1\leq x_{1}<x_{2}<\ldots<x_{m}\leq L}\left(\prod_{x\notin\{x_{1},\ldots,x_{m}\}}\delta_{\tau_{x},N}\right)\sum_{b_{1},\ldots,b_{m}=1}^{N-1}\left(\prod_{k=1}^{m}\delta_{\tau_{x_{k}},b_{k}}-\delta_{\tau_{x_{k}},N}\right)\prod_{k=1}^{m}\mathbbm{1}_{\{Y_{x_{k}}=b_{k}\}}
The above sum can be extended from $m=0$ since all the terms before $m=0,\ldots,\ell-1$ are vanishing. 

@@

			\Psi(\bm{\tau})=&\sum_{m=0}^{L}\sum_{1\leq x_{1}<x_{2}<\ldots<x_{m}\leq L}\left(\prod_{x\notin\{x_{1},\ldots,x_{m}\}}\delta_{\tau_{x_{k}},N}\right)\sum_{b_{1},\ldots,b_{m}=1}^{N-1}\left(\prod_{k=1}^{m}\delta_{\tau_{x_{k}},b_{k}}-\delta_{\tau_{x_{k}},N}\right)\nonumber\\

@@

		indicates that in positions $x_{1},\ldots,x_{m}$ we have particles of species $b_{1},\ldots,b_{m}$ and we have holes $N$ in all other positions.} %{given $\bm{\tau}$ from the bra-vector $\langle \bm{\tau}|$}☺ introduced before equation \eqref{Tensor-S1},} for all $b\in \{0,\ldots,L\}$ and for all $1\leq q_{1}<\ldots<q_{b}\leq L$ {at sites $q_{k}$ (for $k=1,\ldots,b$) we have a particle of type $a_{k}$, while at the other sites the occupation $\tau_{x}$ is left unchanged  ($x\notin\{q_{1},\ldots,q_{b}\}$). }  One can check that equation \eqref{implicit-PSI-PSIp} is indeed formula \eqref{implicit-mass-function} of Corollary~\ref{Corollary-NESS-ABS}. 

>>>>

	\sum_{m=0}^{L}\;\sum_{1\leq x_{1}<x_{2}<\ldots<x_{m}\leq L}\left(\prod_{x\notin\{x_{1},\ldots,x_{m}\}}\delta_{\tau_{x},N}\right)\sum_{b_{1},\ldots,b_{m}=1}^{N-1}\left(\prod_{k=1}^{m}(\delta_{\tau_{x_{k}},b_{k}}-\delta_{\tau_{x_{k}},N})\right)\mathbb{E}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{Y_{x_{k}}=b_{k}\}}\right]

@@

 	Here we have only one term corresponds to $m=2$ in formula  \eqref{implicit-mass-function}.

@@

	{\color{blue}In the last equality we have two terms: the first corresponds to $m=1$ (with $x_{1}=1$) and the second corresponds to $m=2$ in formula \eqref{implicit-mass-function}.}

@@

 	{\color{blue}In the last equality we have four terms: the first term corresponds to $m=0$, the second and the third term correspond to $m=1$ (with $x_{1}=1$ and $x_{1}=2$ respectively) and the fourth term corresponds to $m=2$ in formula \eqref{implicit-mass-function}. }

@@

{\color{blue}In the right-hand-side of the equation above the first addend is the product of the indicator of $\ell$ sites, since none of the empty sites of the configuration $\bm{\tau}$ has been considered. Similarly, the second addend is the product of the indicator of $\ell+1$ occupied sites. Indeed, in addition to the $\ell$ occupied sites of the configuration $\bm{\tau}$, one empty site is in turn chosen and its hole is filled with all possible species particles. The idea is repeated in the next addends with $2,3,...L-\ell$ empty sites that are, in turn, filled with all possible species of particles. We notice that the exponent of the factors (-1) is given by the number of holes that have been filled with all possible species of particles. We introduce an index $m\in \{\ell,\ell+1,\ldots,L\}$ that counts the number of correlated site and we define the coordinates $1\leq x_{1}<x_{2}<\ldots<x_{m}\leq L$. Then, we associate to to each of these $m$ one of the addend in \eqref{sum}. In particular, for $m=\ell$ we associate the first addend and we rewrite it as
		\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{Y_{x}=\tau_{x}\}}=&%\sum_{1\leq x_{1}<\ldots<x_{\ell}\leq L}\;\left(\prod_{k=1}^{\ell}(1-\delta_{\tau_{x_{k}},N})\right)\sum_{b_{1},\ldots,b_{\ell}=1}^{N-1}\left(\prod_{k=1}^{\ell}\delta_{\tau_{x_{k}},b_{k}}\right)\left(\prod_{k=1}^{\ell}\mathbbm{1}_{\{Y_{x_{k}}=b_{k}\}}\right)\nonumber
	%\\	=&
		\sum_{1\leq x_{1}<\ldots<x_{\ell}\leq L}\;\left(\prod_{x\notin \{x_{1},\ldots,x_{\ell}\}}\delta_{\tau_{x},N}\right)\sum_{b_{1},\ldots,b_{\ell}=1}^{N-1}\left(\prod_{k=1}^{\ell}(\delta_{\tau_{x_{k}},b_{k}}-\delta_{\tau_{x_{k},N}})\right)\left(\prod_{k=1}^{\ell}\mathbbm{1}_{\{Y_{x_{k}}=b_{k}\}}\right)
	Similarly, the second addend in \eqref{sum} is associated to $m=\ell +1$ and it is rewritten as 

@@

		\sum_{1\leq x_{1}<\ldots<x_{\ell+1}\leq L}\;\left(\prod_{x\notin \{x_{1},\ldots,x_{\ell+1}\}}\delta_{\tau_{x},N}\right)\sum_{b_{1},\ldots,b_{\ell+1}=1}^{N-1}\left(\prod_{k=1}^{\ell+1}(\delta_{\tau_{x_{k}},b_{k}}-\delta_{\tau_{x_{k},N}})\right)\left(\prod_{k=1}^{\ell+1}\mathbbm{1}_{\{Y_{x_{k}}=b_{k}\}}\right)

@@

\sum_{m=\ell}^{L}\;\sum_{1\leq x_{1}<x_{2}<\ldots<x_{m}\leq L}\left(\prod_{x\notin\{x_{1},\ldots,x_{m}\}}\delta_{\tau_{x},N}\right)\sum_{b_{1},\ldots,b_{m}=1}^{N-1}\left(\prod_{k=1}^{m}(\delta_{\tau_{x_{k}},b_{k}}-\delta_{\tau_{x_{k}},N})\right)\left(\prod_{k=1}^{m}\mathbbm{1}_{\{Y_{x_{k}}=b_{k}\}}\right)
The above sum can be extended until $m=0$ since all the terms $m=0,\ldots,\ell-1$ are vanishing. 

@@

			\Psi(\bm{\tau})=&\sum_{m=0}^{L}\sum_{1\leq x_{1}<x_{2}<\ldots<x_{m}\leq L}\left(\prod_{x\notin\{x_{1},\ldots,x_{m}\}}\delta_{\tau_{x},N}\right)\sum_{b_{1},\ldots,b_{m}=1}^{N-1}\left(\prod_{k=1}^{m}(\delta_{\tau_{x_{k}},b_{k}}-\delta_{\tau_{x_{k}},N})\right)\nonumber\\

@@

		indicates that in positions $x_{1},\ldots,x_{m}$ there are particles of species $b_{1},\ldots,b_{m}$, while there are holes $N$ in all other positions.} %{given $\bm{\tau}$ from the bra-vector $\langle \bm{\tau}|$}☺ introduced before equation \eqref{Tensor-S1},} for all $b\in \{0,\ldots,L\}$ and for all $1\leq q_{1}<\ldots<q_{b}\leq L$ {at sites $q_{k}$ (for $k=1,\ldots,b$) we have a particle of type $a_{k}$, while at the other sites the occupation $\tau_{x}$ is left unchanged  ($x\notin\{q_{1},\ldots,q_{b}\}$). }  One can check that equation \eqref{implicit-PSI-PSIp} is indeed formula \eqref{implicit-mass-function} of Corollary~\ref{Corollary-NESS-ABS}. 
